\section*{Declaration}
This dissertation is submitted in part fulfilment of the requirements for the degree of \degreename
in \coursename of the University of Strathclyde. 

I declare that this dissertation embodies the results of my own work and that it has been composed by myself. 

Following normal academic conventions, I have made due acknowledgement to the work of others. 

I declare that I have sought, and received, ethics approval via the Departmental Ethics Committee as appropriate to my research. 

I give permission to the University of Strathclyde, Department of \deptname, to provide copies of the dissertation, at cost, to those who may in the future request a copy of the dissertation for private study or research. 
and permit  Department of \deptname at the University of Strathclyde to place a copy of the dissertation in a publicly available archive. 

% Change this as needed,
(please tick) Yes [X] No [\quad] 

I declare that the page count for this dissertation (including title page, declaration, abstract, acknowledgements, table of contents, list of illustrations, and references  is XXX pages. % MUST BE 50 or LESS

I understand that project markers are not obliged to read any appendices I include in this dissertation.


I confirm that I wish this to be assessed as a Type 1 2 \circled{3}  Dissertation (please circle).

{\small 1=Software Development;
2=Experimentation-based with Significant Software Development;
3=Experiment-based.}


\begin{tabular}{|c|p{8cm}|}
\hline
 Signature:    &  \\ \hline
 Date:    & \\ \hline
\end{tabular}

